Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-02 paper/main.tex
more updates to the paper

\subsubsection{UMM}
%
UMM uses the same budget of evaluations ($\FEmax$) as CEGO
and initially samples $\minit=10$ solutions uniformly. The other two parameters
of UMM are $r_1$ and $r_2$, which determine the balance between exploration and
exploitation. In the experimental section we will study their impact. %implemented UMM using Python 3.
At each sampling step, we set $\beta=10$, meaning that 10 permutations are generated and the farthest from $S$ is selected for evaluation.

@@

\subsubsection{Other settings}
%
For simplicity, we use Kendall's-$\tau$
distance~(Eq.~\ref{eq:kendall_decomp}) in all experiments. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance and the same may apply to UMM.
We plan to extend UMM to other distance measures in the future.  In all
experiments, we consider a maximum budget of $\FEmax=400$ evaluations of the
actual objective function. In a white-box context, state-of-the-art algorithms
for the problems considered here typically evaluate thousands of solutions,
thus, the budget considered here for the black-box context is extremely
limited.

\subsubsection{Benchmark problems}
%
Experiments with real-world expensive black-box problems would be computationally infeasible. Instead, we consider classical combinatorial optimization problems as black-box optimization problems. \ekhine{cambio la definition de LOP}{In this section, and following the consensus on the optimization literature, the permutations denote orderings. }

The \emph{Linear Ordering Problem (LOP)}, when minimizing, is defined as
%\footnote{For consistency with the other problems, we minimise the lower triangle instead of maximising the upper triangle.} 
\begin{equation}\label{eq:lop}
  \min_{\sigma \in S_n} f(\sigma) = \sum_{i=1}^{n} \sum_{j=1}^{i-1}  a_{\sigma(i), \sigma(j)}
\end{equation}
where $[a_{i,j}]$ is a matrix of size $n \times n$ and $\sigma^{-1}$ is the inverse of $\sigma$.

The \emph{Quadratic Assignment Problem (QAP)} is defined by:
\begin{equation}\label{eq:qap}
  \min_{\sigma \in S_n} f(\sigma) = \sum_{i=1}^n \sum_{j=1}^n a_{i,j} b_{\sigma(i), \sigma(j)}
\end{equation}
%
where $[a_{i,j}]$ and $[b_{i,j}]$ are two matrices of size $n \times n$.

>>>>

\subsubsection{UMM}
%
UMM uses the same budget of evaluations ($\FEmax$) as CEGO and initially
samples $\minit=10$ solutions uniformly.  At each sampling step, we set
$\beta=10$, meaning that 10 permutations are generated and the farthest from
$S$ is selected for evaluation.  The other two parameters of UMM are $r_1$ and
$r_2$, which determine the balance between exploration and exploitation. In the
experimental section we will study their impact.

@@

\subsubsection{Other settings}
%
For simplicity, we use Kendall's-$\tau$
distance~(Eq.~\ref{eq:kendall_decomp}) in all experiments.
%Nevertheless,
%\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
%when using Hamming distance and the same may apply to UMM.
We plan to extend UMM to other distance measures in the future.  In all
experiments, we consider a maximum budget of $\FEmax=400$ evaluations of the
actual objective function. In a white-box context, state-of-the-art algorithms
for the LOP and PFSP typically evaluate thousands of solutions,
thus, the budget considered here for the black-box context is extremely
limited.

\subsubsection{Benchmark problems}
%
Experiments with real-world expensive black-box problems would be computationally infeasible. Instead, we consider classical combinatorial optimization problems as black-box optimization problems. \ekhine{cambio la definition de LOP}{In this section, and following the consensus on the optimization literature, the permutations denote orderings. }\MANUEL{That seems strange, shouldn't be use the same everywhere? I would rather use rankings or orderings everywhere and I have a slight preference for orders since this is an optimization paper.}

The \emph{Linear Ordering Problem (LOP)}, when minimizing, is defined as
%\footnote{For consistency with the other problems, we minimise the lower triangle instead of maximising the upper triangle.} 
\begin{equation}\label{eq:lop}
  \min_{\sigma \in S_n} f(\sigma) = \sum_{i=1}^{n} \sum_{j=1}^{i-1}  a_{\sigma(i), \sigma(j)}
\end{equation}
%
where $[a_{i,j}]$ is a matrix of size $n \times n$ \manuel{and $\sigma^{-1}$ is the inverse of $\sigma$}{}.

% The \emph{Quadratic Assignment Problem (QAP)} is defined as
% \begin{equation}\label{eq:qap}
%   \min_{\sigma \in S_n} f(\sigma) = \sum_{i=1}^n \sum_{j=1}^n a_{i,j} b_{\sigma(i), \sigma(j)}
% \end{equation}
% %
% where $[a_{i,j}]$ and $[b_{i,j}]$ are two matrices of size $n \times n$.
